---
title: "Querying from the Halodotapi endpoints"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{querying-api}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
suppressMessages({
    suppressWarnings({
        library(halodotapi)
        library(dplyr)
    })
})
```

# Developing the API endpoints

At current there are four API endpoints related to player performance and match session information:

* `api_match_details()`
* `api_player_csr()`
* `api_player_match_history()`
* `api_player_service_record()`

These functions develop the URL's required to perform queries. These are
generally not intended to be used directly, but can be used in the event the
user wishes to handle the responses themselves.

So long as a valid API token is present in the R environment (either by
configuring the `.Renviron` file, or by setting `Sys.setenv()`), the api
functions will bundle the authentication header with the URL. The environment
variable is named `AUTOCODE_API_KEY`.

If you don't have one, you can obtain one by navigating to https://autocode.com/
and registering for an account. Go to your Profile > Account > Identity Tokens >
General Use Identity Tokens and click "Create General Use Identity"

## Example endpoint

The output from the `api_` functions are a httr2_request object. Passing these
objects to `httr2::req_perform` will obtain the response from the server. The
body is typically extracted in this package using `httr2::resp_body_json`, but
other functions such as `resp_body_string`, or similar could be used.

```{r}
api_player_match_history("Corvus0805", count = 25L, offset = 0L, mode = 'matchmade')
```

# Querying from the API

The API URL generation, request, and responses are handled for you by the `get_`
family of functions. There is one for each endpoint, and these will be the
workhorses of the package typically used by users:

* `get_match_details()`
* `get_player_csr()`
* `get_player_match_history()`
* `get_player_service_record()`

## Example: obtaining the player service record

As an example, we'll pull my service record. There are two items; medals, and
statistics.

```{r}
service_record = get_player_service_record("Corvus0805", type = "multiplayer", filter = "all")
```

The statistics is a data frame with a single record, with all-time summary statistics on my player performance.

```{r}
str(service_record$stats)
```

The medals item is a data frame with several records, one for each unique medal earned, and frequencies of said medals.

```{r}
head(arrange(service_record$medals, desc(count)))
```

The result is a data frame of one record, displaying all-time summary statistics
for the gamertag.
